---
title: "Visiting São Paulo for My American Friends"
author: "PR"
date: "6/23/2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

## Map of São Paulo

```{r map, echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, comment=""}
library(leaflet)
set.seed(2019-06-26)
#myIcon <- makeIcon(
#    iconURL = '',
#    iconWidth = 80, iconHeight = 30,
#    iconAnchorX = 40, iconAnchorY = 15
#)

my_Sao_Paulo_LatLong <- data.frame(lat = c(-23.5829,-23.5614,-23.598913,-23.585,-23.5582,-23.5915),
                                   lng = c(-46.6825,-46.6559,-46.687575, -46.6625,-46.666,-46.6895),
                                   col=c('blue','red','green','red', 'red','green'))

## add multiple popups
spSites <- c(
    "<a href='https://www.transamerica.com.br/nossos-hoteis/transamerica-executive-faria-lima/'>Transamerica Flat Itaim Bibi</a>",
    "<a href='http://masp.art.br/'>Museum of Art São Paulo</a>",
    "<a href='https://fogodechao.com.br/'>Fogo de Chão Brazilian Steakhouse</a>",
    "<a href='https://parqueibirapuera.org/ibirapuera-park/'>Ibirapuera Park</a>",
    "<a href='http://omalleysbar.net/'>O'Malley's Pub</a>",
    "<a href='http://www.jkshoppingdf.com.br/'>Shopping JK</a>"
)

my_Sao_Paulo_LatLong %>%
    leaflet() %>%
    addTiles() %>%
    addCircleMarkers(clusterOptions = markerClusterOptions(),popup=spSites,color=my_Sao_Paulo_LatLong$col) %>%
    addLegend(labels= c('Residence','Leisure','Shopping/Dining','Safe Zone'), colors=c('blue','red','green','gray')) %>%
    addRectangles(lat1=-23.54,lng1=-46.69,
                  lat2=-23.62,lng2=-46.64,color=c('gray'))

#my_Sao_Paulo_LatLong


```


## Points of Interest Inside City

For a short visit, I recommend staying within or close to the area shown in gray rectangle

- except for upper right corner, which is near to some sketchy areas of *Centro*, this area is generally **safe** even at night

The map on previous page shows some points of interest:

1. **Transamerica Flat** - place to stay in walkable neighborhood
2. **JK Shopping** - new high-end mall 
3. **Fogo do Chão** - Brazilian Steakhouse
4. **Museum of Art** - located on Paulista Avenue, one of the city's major cultural centers
5. **O'Malley's** - Irish pub popular among tourists and locals 
6. **Ibirapeura Park** - great for walking, biking, etc.

 

